---
title: "Investigating Vocational Teachers' Informal Workplace Learning Using Experience Sampling"
author: "Manuel Böhm"
date: '`r Sys.Date()`'
output:
  pdf_document:
    latex_engine: xelatex
    toc: true
    toc_depth: 2
  html_document:
    toc: true
    toc_depth: '2'
    df_print: paged
  word_document: default
bibliography:
- _bib/references.bib
- _bib/grateful-refs.bib
csl: _bib/apa.csl
link-citations: true
toc: true
toc-title: Article Outline
header-includes: \pagenumbering{gobble}
numbersections: true
---

\newpage
\pagenumbering{arabic}

# Acknowledgement {.unnumbered}

-   Frau Banschbach (falls ich die Daten von ihr hier verwende)

# Possible Journals {.unnumbered}

-   Teaching and Teacher Education (IF: 4.0)

-   Human Resource Development International (IF: 3.8)

    -   <https://doi.org/10.1080/13678860010004123> was also published here

-   Journal of Workplace Learning (IF: )

-   Vocations and Learning (IF: 1.9)

-   Learning Environments Research (IF: 2.7)

-   Technology, Knowledge and Learning (IF: 3.0) - not that fitting...

-   Empirical Research in Vocational Education and Training (IF: 1.6)

\newpage

# Abstract {.unnumbered}

...

Keywords: ...

\newpage

# Introduction

According to @rauschUsingDiariesResearch2014, ...

Research Questions

1.  RQ (learning, stress and coping across activities, control for age, sex, jobscope) - MLM

    Which of teachers' daily work activities are perceived as (a) the most conducive to learning? (b) Which are perceived as the most stressful and (c) with which of the stresful activities could the teachers cope the best?

2.  RQ (group activity categories: social, reflection, ...) and conduct an anova to check for significant differences)

    Can the learning-fostering characteristics ... be found in the activity categories? Are there significant differences between these categories?

3.  RQ (Karasek, control for age, sex, jobscope) - MLM

    Do stress and coping predict informal learning in teachers' daily work activities, as stated in Karasek's learning hypothesis?

    H: according to Karasek

4.  RQ (Time effect) H: higher participation -\> bigger pc_learn

    Can time effects be found in the data? Does continued experience sampling have an effect on perceived informal learning?

5.  [Desription of the Learning (freetext fields, Banschbach)]

# Research on Teachers' Workplace Learning

## Characteristics of the Teacher Profession and their Daily Work Activities

### Characteristics

### Teachers' Daily Work Activities

## Teachers' WPL

-   Billett?!
-   Lazarus & Folkman (for Stress)
-   Karasek
    -   Studies on Karasek
        -   The Job Demand-Control (-Support) Model and psychological well-being: A review of 20 years of empirical research (<https://doi.org/10.1080/026783799296084>)
        -   

1.  Billett and others (which characteristics of the situation and the activity foster learning?!)

2.  Consideration of stress (Karasek, ...)

    use stress as a characteristic of activities to introduce Karasek (and briefly talk about negative consequences: Lazarus & Folkman)

get con concrete: Teachers' Learning Activities

# Description of the Empirical Study

## Sample and Acquisition of Participants

## Measurements Used in the Diary Study

-   Description of the Developed Task Framework

## Procedure of the Diary Study

## Data Processing and Analysis

```{r maintenance, eval=FALSE, include=FALSE}
source("_src/maintenance.R", local = knitr::knit_global())
```

```{r session start, include=FALSE}
## Load and install packages (using package manager)
if (!require("pacman")) {
  install.packages("pacman")
  library(pacman)
}
pacman::p_load(papaja, knitr, dplyr, remotes, lme4, tidyr, kableExtra,
               modelsummary, performance, stats, lmerTest, ggplot2, corrr,
               parameters, car, psych, jtools, grateful, blockTools,
               robustlmm, usethis, gitcreds, stringr, HLMdiag, lmtest, effects, 
               sjPlot, devtools, rmdwc) 

# install.packages("robustlmm", dependencies = TRUE)
# install.packages("broom.mixed", dependencies = TRUE)

```

```{r load files, include=FALSE}
# welcome questionnaire
welcome_raw <- read.csv2("_data/raw/20221018_1718_1_AARL-BS Willkommen.csv")
# activities questionnaire
activities_raw <- read.csv2("_data/raw/20221018_1717_2_AARL-BS Taetigkeiten_de102944944440141306.csv")
# jobscope
jobscope <- read.csv2("_data/jobscope.csv", na = "?")
# jobscope correction
jobscope_correction <- read.csv2("_data/jobscope_v3.csv")
```

```{r data prep, include=FALSE}
source("_src/data_prep_welcome.R", local = knitr::knit_global())
source("_src/data_prep_activities.R", local = knitr::knit_global())
```

# Results

## RQ1

```{r, include=FALSE}


```

## RQ2

```{r}

```

## RQ3

```{r}

```

# Conclusion

\newpage

# Data availability statement

The anonymized data are available on github under the following link: ...\

–\> Remove Email Addresses from the raw data and make it available online.

# References

::: {#refs custom-style="Bibliography"}
:::

\newpage

# Appendix
