---
title: "Investigating Vocational Teachers' Informal Workplace Learning Using Experience Sampling"
author: "Manuel Böhm"
date: '`r Sys.Date()`'
output:
  pdf_document:
    latex_engine: xelatex
    toc: true
    toc_depth: 2
  html_document:
    toc: true
    toc_depth: '2'
    df_print: paged
  word_document: default
bibliography:
- _bib/references.bib
- _bib/grateful-refs.bib
csl: _bib/apa.csl
link-citations: true
toc: true
toc-title: Article Outline
header-includes: \pagenumbering{gobble}
numbersections: true
---

\newpage
\pagenumbering{arabic}

# Acknowledgement

-   Banschbach (falls ich die Daten von ihr hier verwende)

# Abstract

# Introduction

According to @rauschUsingDiariesResearch2014, ...

Research Questions

1.  RQ (learning across activities, control for age, sex, jobscope) - MLM

2.  RQ (group activity categories: social, reflection, ...) and conduct an anova to check for significant differences)

3.  RQ (Karasek, control for age, sex, jobscope) - MLM

    H: according to Karasek

4.  RQ (Time effect) H: higher participation -\> bigger pc_learn

5.  Desription of the Learning (freetext fields, Banschbach)

# Research on Teachers' Workplace Learning 

## Characteristics of the Teacher Profession 

### Characteristics

### Teachers' Daily Work Tasks

### Teachers' Learning Activities

## Teachers' WPL

-   Billett?!
-   Lazarus & Folkman (for Stress)
-   Karasek

1.  Billett and others (which characteristics of the situation and the activity foster learning?!)

2.  Consideration of stress (Karasek, ...)

    use stress as a characteristic of activities to introduce Karasek (and briefly talk about negative consequences: Lazarus & Folkman)

# Method

## Description of the Developed Task Framework

```{r maintenance, eval=FALSE, include=FALSE}
source("_src/maintenance.R", local = knitr::knit_global())
```

```{r session start, include=FALSE}
## Load and install packages (using package manager)
if (!require("pacman")) {
  install.packages("pacman")
  library(pacman)
}
pacman::p_load(papaja, knitr, dplyr, remotes, lme4, tidyr, kableExtra,
               modelsummary, performance, stats, lmerTest, ggplot2, corrr,
               parameters, car, psych, jtools, grateful, blockTools,
               robustlmm, usethis, gitcreds, stringr, HLMdiag, lmtest, effects, 
               sjPlot) 

# install.packages("robustlmm", dependencies = TRUE)
# install.packages("broom.mixed", dependencies = TRUE)
```

```{r load files, include=FALSE}
# welcome questionnaire
welcome_raw <- read.csv2("_data/raw/20221018_1718_1_AARL-BS Willkommen.csv")
# activities questionnaire
activities_raw <- read.csv2("_data/raw/20221018_1717_2_AARL-BS Taetigkeiten_de102944944440141306.csv")
# jobscope
jobscope <- read.csv2("_data/jobscope.csv", na = "?")
# jobscope correction
jobscope_correction <- read.csv2("_data/jobscope_v3.csv")
```

```{r data prep, include=FALSE}
source("_src/data_prep_welcome.R", local = knitr::knit_global())
source("_src/data_prep_activities.R", local = knitr::knit_global())
```

# Results

## RQ1

```{r, include=FALSE}


```

## RQ2

```{r}

```

## RQ3

```{r}

```

# Conclusion

\newpage

# References

::: {#refs custom-style="Bibliography"}
:::

\newpage

# Appendix
